### 2017-08-07 src/4_OnlineLearning.tex
REVISAR DESDE P38 L6

\noindent where $\mathcal{H}$ is called the {\em hypothesis space}, i.e. the space
of functions that the algorithm is allowed to search. The selection of
$f$ is based on the minimization of the expected error of the loss
function $V(f(x),y): Y \times Y$ defined as:

@@

A very complex models will fit the training data better (low bias) but it could
overfit it and generalise poorly (high variance), this is also called the
bias-variance tradeoff.  Generalisation accuracy can sometimes be improved with
more training data. The figure \ref{fig:tradeoff} illustrates how generalisation
accuracy depends on the complexity of the model and the amount of training data.

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.8\textwidth]{img/3tradeoff}
  \caption{Tradeoff in empirical learning from \cite{dietterich2003}. The generalization accuracy is not affected by the amount of examples for low complex classifiers. However, for some more complex classifiers, the number of examples improves the generalization accuracy. The key is to find the best generalization accuracy and the lowest complex classifier as possible. }
  \label{fig:tradeoff}
\end{figure}

@@

@@

The bias shown in equation \ref{eq:biastrade} can be obtain through resampling of the input data $x$, therefore an average of the predicted values can be calculated. If these prediction values are substantially different to the true value, the bias will be high.

The error due to variance is the amount by which the prediction, over one training set, differs from the expected predicted value, over all the training sets. Variance measures how inconsistent are the predictions from one another, over different training sets, not whether they are accurate or not \cite{gutierrez2015machine}.
%=======================HASTA ACA REVISADO PROFE =========================

The generalisation error is unknown, but it can be estimated using a training sample, a testing sample or by estimating the model complexity. Figure \ref{fig:traintesterror} shows prediction error for training and testing sample.  In general, in the training sample prediction error is decreasing with more complex models but it overfit the data and it is not a good model for the test data. Figure \ref{fig:bvtradeoff} shows how testing error can be decomposed into bias and variance components. The best model will be the one has a balance between bias and variance.

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.8\textwidth]{img/model_complexity}
  \caption{Training and test error. Image source is \cite{friedman2001elements}}
  \label{fig:traintesterror}
\end{figure}

The objective is to simultaneously reduce bias and variance as much as possible in order to obtain as accurate model as is feasible.  However, there is a tradeoff to be made when selecting models. Models that exhibit small variance and high bias underfit the truth target.  Models that exhibit high variance and low bias overfit the truth target.

This bias-variance tradeoff is the reason why in order to obtain the best model, data is usually broken in three subsets: training set, validation set and testing set. Training set is used to determine the model, validation set is used to estimate the generalisation error and finally testing set is used to estimate the accuracy of the model. Usually the partition is 50\% for training set, 25\% for validation and 25\% for testing purposes. This procedure can be extended to a Cross Validation (CV) procedure \cite{geisser1975}, usually used when the amount of data is limited. Various splitting strategies lead to various CV estimates. In K-fold cross-validation the training data is divided randomly into K distinct subsets, then the network is trained using K-1 subsets, and tested on the remaining subset. The process of training and testing is then repeated for each of the K possible choices of the subset omitted from the training. The average performance on the K omitted subsets is then our estimate of the generalisation performance.

@@

@@

\subsection{Regularization}\label{sec:regularization}

>>>>

\noindent where $\mathcal{H}$ is called the {\em hypothesis space}, i.e. the space
of functions that the algorithm is allowed to search. The selection of
$f$ is based on the minimisation of the expected error of the loss
function $V(f(x),y): Y \times Y$ defined as:

@@

The relationship between generalisation error and the amount of training or
input data is intuitive: the more data is given to the learning model $f$, the
more evidence the algorithm has about the problem. In the limit, the input data
will contain every possible example, so the algorithm will generalize perfectly.
However, for some $f \in H$, the best hypothesis $\hat{f}$ might be far away to
the best hypothesis class but it is the best that all the learners can hope.
Therefore, to choose the right hypothesis class $H$ is crucial. The error of
this best hypothesis is formalised as the {\em approximation or generalisation
error} \cite{niyogi1996relationship}.

Additionally, we do not have infinite data but only some finite random sample
set to find an hypothesis, the additional error caused by finiteness of the
data, is called {\em estimation error}. The amount of data needed to ensure a
small {\em estimation error} is referred to as {\em sample complexity} of the
problem.

The relationship between the generalisation error and the hypothesis complexity
is less intuitive. If the class $H$ complexity (VC dimension) increases, then to
mantain an {\em estimation error}, the {\em sample complexity} increases.
Therefore, if we have a low complex model we will reduce the {\em sample complexity}
but it will increase {\em generalisation error}. The hypothesis has to be
sufficiently complex to capture the characteristics of the data.

The figure \ref{fig:tradeoff} illustrates how generalisation
accuracy depends on the complexity of the model and the amount of training data.

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.8\textwidth]{img/3tradeoff}
  \caption{Tradeoff in empirical learning from \cite{dietterich2003}. The
generalization accuracy is not affected by the amount of examples for low
complex classifiers. However, for some more complex classifiers, the number of
examples improves the generalization accuracy. The key is to find the best
generalization accuracy and the lowest complex classifier with the available
training data. }
  \label{fig:tradeoff}
\end{figure}

@@

A very complex models will fit the training data better (low bias) but it could
overfit it and generalise poorly (high variance), this is also called the
bias-variance tradeoff.

Figure \ref{fig:traintesterror} shows {\em prediction or estimation error} for
training and testing sample.  In general, in the training sample prediction
error is decreasing with more complex models but it overfit the data and it is
not a good model for the test data.

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.8\textwidth]{img/model_complexity}
  \caption{Training and test error. Image source is
\cite{friedman2001elements}.The blue curve represents the training error which
decreases with more complex models. However, the model starts to overfit the
data reducing the generalisation capacity of the model,this occurs when the
prediction error in the test sample starts to increase (red curve).}
  \label{fig:traintesterror}
\end{figure}

@@

Figure \ref{fig:bvtradeoff} shows how
testing error can be decomposed into bias and variance components. 
The bias shown in equation \ref{eq:biastrade} can be obtain through resampling
of the input data $x$, therefore an average of the predicted values can be
calculated. If these prediction values are substantially different to the true
value, the bias will be high.

@@

The error due to variance is the amount by which the prediction, over one
training set, differs from the expected predicted value, over all the training
sets. Variance measures how inconsistent are the predictions from one another,
over different training sets, not whether they are accurate or not
\cite{gutierrez2015machine}.

This bias-variance tradeoff is the reason why, in order to obtain the best model,
data is usually broken in three subsets: training set, validation set and
testing set. Training set is used to determine the model, validation set is used
to estimate the generalisation error and finally testing set is used to estimate
the accuracy of the model. Usually the partition is 50\% for training set, 25\%
for validation and 25\% for testing purposes. This procedure can be extended to
a Cross Validation (CV) procedure \cite{geisser1975}, usually used when the
amount of data is limited. Various splitting strategies lead to various CV
estimates. In K-fold cross-validation the training data is divided randomly into
K distinct subsets, then the network is trained using K-1 subsets, and tested on
the remaining subset. The process of training and testing is then repeated for
each of the K possible choices of the subset omitted from the training. The
average performance on the K omitted subsets is then our estimate of the
generalisation performance.

@@

%=======================HASTA ACA REVISADO PROFE =========================
\subsection{Regularization}\label{sec:regularization}
